---
name: Sam Abbott
position: ""
address: "Bristol Medical School: Population Health Sciences, University of Bristol"
phone: 
www: samabbott.co.uk
email: contact@samabbott.co.uk
twitter: seabbs
github: seabbs
aboutme: "Dynamic modeller and data scientist focussing on infectious disease dynamics, epidemiology, and control. I have a strong interest in reproducibility and tool development, having developed multiple widely used packages and dashboards. My work lies at the interface between dynamic modelling, statistical modelling and data science - incorporating elements from software development to enhance robustness and longevity."
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 000000
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
source("../scripts/install.R")
```

```{r get data, include=FALSE}
## Education
edu <- read_csv(here("data", "education.csv"))

## Jobs
jobs <- read_csv(here::here("data", "jobs.csv"))

## Publications - change google id here
pubs <- scholar::get_publications("GqZm90IAAAAJ") %>% 
  dplyr::mutate(author = author %>% 
                  as.character %>% 
                  stringr::str_trim(),
                journal = journal %>% 
                  replace(journal %in% "bioRxiv", "BioRxiv"), 
                first_author = case_when(stringr::str_starts(author, "S Abbott") ~ TRUE,
                                         TRUE ~ FALSE),
                preprint = case_when(journal %in% c("bioRxiv", "BioRxiv") ~ TRUE,
                                         TRUE ~ FALSE)) %>% 
  dplyr::arrange(desc(year))

## Software
software <- read_csv(here::here("data", "software.csv")) %>% 
  arrange(desc(when)) 

## Dashboards
dashboards <- read_csv(here::here("data", "dashboards.csv")) %>% 
  arrange(desc(when)) 

## Teaching
teaching <- read_csv(here::here("data", "teaching.csv")) %>% 
  arrange(desc(when))

## Presentations
presentations <- read_csv(here::here("data", "presentations.csv")) %>% 
  arrange(desc(when))

## Training
training <- read_csv(here::here("data", "training.csv")) %>% 
  arrange(desc(end))

## Skills
skills <- read_csv(here::here("data", "skills.csv")) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = ", ")) %>% 
  ungroup %>% 
  unique

## Service
service <- read_csv(here::here("data", "service.csv"))
```

# Education 

```{r}
detailed_entries(edu, 
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = loc,
                 with = uni,
                 why = details,
                 .protect = FALSE)

```

# Experience

```{r research}
jobs %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = company,
    where = where,
    why = details,
    .protect = FALSE
  )
```

# Skills

```{r}
skills %>% 
  detailed_entries(what = skill, with = category)
```

\pagebreak

# Training

```{r}
training %>% 
  detailed_entries(what = what, with = with, when = when, where = where, why = why)
```


# Teaching

```{r}
teaching %>% 
  detailed_entries(what = what, when = when, with = with, where = where, why = why)
```


# Service


```{r}
service %>% 
  detailed_entries(with = type, why = details)
```


# Publications

**First author**

```{r}
pubs %>% 
  dplyr::filter(first_author, !preprint) %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

**Non-first author**

```{r}
pubs %>% 
  dplyr::filter(!first_author, !preprint) %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

**Preprints**

```{r}
pubs %>% 
  dplyr::filter(preprint) %>% 
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

*This list is updated programmatically each week. See [my Google Scholar](https://scholar.google.com/citations?user=GqZm90IAAAAJ&hl=en) for DOIs and citation details.*

# Selected Software

**`R` Packages**

```{r}
software %>% 
  detailed_entries(what = what, with = package, when = when, where = where, why = why)
```

**Interactive tools**

```{r}
dashboards %>% 
  dplyr::mutate(with = what, 
                what = why) %>% 
  detailed_entries(what = what, with = with, when = when, where = where)
```

*See [my GitHub](https://github.com/seabbs/) for a complete overview of my software both released and in development.*

# Presentations

```{r}
presentations %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where,
                   why = why,
                   .protect = TRUE)
```

