---
name: Sam Abbott
position: "Research Fellow"
address: "London School of Hygiene and Tropical Medicine"
phone: 
www: samabbott.co.uk
email: contact@samabbott.co.uk
twitter: seabbs
github: seabbs
aboutme: "My main research interest lies in developing, evaluating, and applying methods for improving our understanding of infectious disease dynamics in real-time. I am committed to doing science in the open, and collaboratively, with the aim of producing useful and actionable output."
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
library(vitae)
library(here)
library(vroom)
library(dplyr)
library(lubridate)
library(glue)
```

```{r get data, include=FALSE}

```

# Positions

```{r research}
jobs <- vroom(here::here("data", "jobs.csv"))

jobs |>
  detailed_entries(
    what = glue("{role} - {company}"),
    when = glue("{start_date}--{end_date}")
)
```


# Qualifications

```{r}
edu <- vroom(here("data", "education.csv"))

detailed_entries(edu,
                 when = glue("{start_date}--{end_date}"),
                 what = glue("{degree} - {uni}"))

```

# Skills

```{r}
skills <- vroom(here::here("data", "skills.csv")) |>
  group_by(category) |>
  mutate(skill = paste(skill, collapse = ", ")) |>
  ungroup() |>
  unique()

skills |>
  detailed_entries(what = skill, with = category)
```

# Selected publications

```{r, eval = FALSE}
pubs <- vroom(here::here("data", "publications.csv")) |>
  arrange(desc(when))

pubs |>
  detailed_entries(
    what = title,
    when = as.character(year),
    with = author,
    where = journal,
    .protect = TRUE
)
```

*See [here](https://scholar.google.com/citations?user=GqZm90IAAAAJ&hl=en) for a full list of my publications.*

# Selected software

```{r}
software <- vroom(here::here("data", "software.csv")) |>
  arrange(desc(when))

software |>
  detailed_entries(
    what = what, with = package, when = when, where = where
)
```

*Software that I have primarily developed has had over 30k downloads and been used in multiple public health organisations such as the WHO and the ECDC. Software that I have managed the development of has had over 20k downloads. See [my GitHub](https://github.com/seabbs/) for more on my software output.*

# Research (Co-) Supervision

# Teaching

```{r}
teaching <- vroom(here::here("data", "teaching.csv")) |>
  arrange(desc(when))

teaching |>
  detailed_entries(
    what = what, when = when, with = with, where = where, why = why
)
```


# Presentations

```{r}
presentations <- vroom(here::here("data", "presentations.csv")) |>
  arrange(desc(when))

presentations |>
  detailed_entries(what = with,
                   when = when
)
```

*See the details, slides, and recordings of my presentations [here](https://samabbott.co.uk/talks.html)*

# Service

```{r}
service <- vroom(here::here("data", "service.csv"))

service |>
  detailed_entries(with = type, why = details)
```
